The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-05 paper.tex
update

\subsection{X-ray}

Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

  \begin{subequations}
     \begin{align}
        &I_{\nu} = \frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
        a(p)\nu^{-0.5(p-1)}.\\
        &a(p)=\nonumber\\
             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
                                        \Gamma\left[\left(3p+9\right)/12\right]\
                                        \Gamma\left[\left(p+5\right)/4\right]}
        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
     \end{align}
  \end{subequations}

>>>>

\subsection{X-ray}
The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

  \begin{subequations}
     \begin{align}
        &\frac{dE}{dtd\nu dV} =\nonumber\\
        &\frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
        a(p)\nu^{-0.5(p-1)}.\\
        &a(p)=\nonumber\\
             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
                                        \Gamma\left[\left(3p+9\right)/12\right]\
                                        \Gamma\left[\left(p+5\right)/4\right]}
        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
     \end{align}
  \end{subequations}
